\documentclass[10pt, letterpaper]{article}

% ================= PACKAGES =================
\usepackage[
    ignoreheadfoot,
    top=2cm,
    bottom=2cm,
    left=2cm,
    right=2cm
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{needspace}
\usepackage{iftex}

% ================= ATS / ENCODING (ALWAYS) =================
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage[final]{microtype}

\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
% ATS FIX: plain dash instead of math bullet
\renewcommand\labelitemi{-}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}

\newenvironment{highlights}{
\begin{itemize}[leftmargin=12pt, itemsep=2pt]
}{
\end{itemize}
}

\hypersetup{
  colorlinks=true,
  urlcolor=black
}

% ================= DOCUMENT =================
\begin{document}

% ================= HEADER =================
{\fontsize{22}{22}\selectfont \textbf{Tamim Hmizi}} \\[4pt]
{\large Full Stack and Cloud DevOps Engineer} \\[6pt]
Ariana, Tunisia \;|\;
\href{mailto:tamimhmizi@icloud.com}{tamimhmizi@icloud.com} \;|\;
+216 21 611 816 \\
\href{https://linkedin.com/in/tamimhmizi}{linkedin.com/in/tamimhmizi} \;|\;
\href{https://github.com/tamim-hmizi}{github.com/tamim-hmizi} \;|\;
\href{https://tamim-hmizi.github.io/Portfolio/}{Portfolio}

\vspace{0.4cm}

% ================= PROFILE =================
\section{Professional Profile}
Full Stack and Cloud DevOps Engineer with \textbf{4+ years of hands-on project experience} spanning freelance work, academic projects, and internships --- now operating in full-time professional roles.
Deep expertise in Kubernetes, Terraform, CI/CD automation, and cloud-native architecture across Azure, AWS, and OpenStack.
Currently consulting for a \textbf{Microsoft CSP Gold Partner} on sovereign cloud and infrastructure security --- delivering \textbf{70\% faster deployments} and \textbf{40\% reduction in manual overhead}.

% ================= SKILLS =================
\section{Core Technical Skills}
\textbf{Cloud and Platforms:} Azure (Stack Hub, AKS, Public), AWS (EKS), GCP, OpenStack, DigitalOcean, Hybrid Cloud, IaaS, PaaS \\
\textbf{Containers and Orchestration:} Docker, Docker Compose, Kubernetes (AKS, EKS, K8s), Helm \\
\textbf{DevOps and Automation:} Terraform, Ansible, Jenkins, GitHub Actions, GitLab CI, CI/CD Pipelines, Infrastructure as Code (IaC), Nexus, Traefik, Portainer \\
\textbf{Monitoring and Observability:} Prometheus, Grafana, ELK Stack, CloudWatch, Custom Python Exporters, Alerting and Metrics Visualization \\
\textbf{Security and Quality:} Fortinet Firewalls, Network Segmentation, IAM, SonarQube, Trivy, MFA, OAuth2, RBAC, Data Encryption \\
\textbf{Backup and Storage:} Commvault, MinIO (Object Storage), Redis (Caching), SQL and NoSQL Backup Strategies \\
\textbf{Systems and Identity:} Linux (Ubuntu, CentOS), Windows Server, Active Directory, Microsoft 365, WSL \\
\textbf{Programming Languages:} TypeScript, JavaScript, Python, Java, C\#, PHP, Bash/Shell, SQL, C++, Assembly \\
\textbf{Backend Architectures:} NestJS, FastAPI, Express.js, Django, Flask, Spring Boot, Node.js, RESTful and WebSocket APIs \\
\textbf{Frontend Architectures:} React (Vite, Next.js), Angular, Vue.js, Vuex, Tailwind CSS v4, Chakra UI, shadcn/ui \\
\textbf{Databases:} PostgreSQL, MongoDB, MySQL, Redis, Prisma, Mongoose, Sequelize, BullMQ (Job Queues)

% ================= EXPERIENCE =================
\section{Professional Experience}

\textbf{Infrastructure Consultant --- RFC (Microsoft CSP and Gold Partner)} \hfill Oct 2025 -- Present \\
Ariana, Tunisia
\begin{highlights}
\item \textbf{Engineered} and optimized \textbf{production hybrid cloud infrastructures} for a leading \textbf{Microsoft Cloud Solution Provider (CSP)}, integrating \textbf{Azure Stack Hub} with public Azure services.
\item \textbf{Architected} sovereign cloud environments for enterprise clients, ensuring strict data residency and compliance via Microsoft-partnered architectures.
\item \textbf{Orchestrated} enterprise-wide security and networking using \textbf{Fortinet SD-WAN} and \textbf{Cisco} logic to protect multi-tenant infrastructure.
\item \textbf{Administered} business-critical backup operations using \textbf{Commvault}, implementing automated restore validation and failure analysis reporting.
\item \textbf{Automated} recurring infrastructure tasks and security patches across Linux and Windows Server fleets, reducing manual overhead by \textbf{40\%}.
\item \textbf{Facilitated} high-level technical workshops as an \textbf{Infrastructure Subject Matter Expert (SME)}, empowering clients on cloud-native security and Microsoft 365 governance.
\end{highlights}

\textbf{DevOps Platform Engineer --- Final Year Project (PFE), RFC} \hfill Feb 2025 -- Aug 2025
\begin{highlights}
\item Designed and implemented a \textbf{DevOps-as-a-Service SaaS platform} to automate application analysis, deployment, and monitoring.
\item Built a \textbf{monolithic core application} using \textbf{React}, \textbf{Express.js}, \textbf{FastAPI}, and \textbf{MongoDB}, with clear separation between frontend, API gateway, and backend services.
\item Integrated an \textbf{AI-driven analysis engine (LLM-based)} to inspect Git repositories, application structure, dependencies, and runtime requirements.
\item Implemented \textbf{multi-architecture deployment logic}, enabling automated decision-making between:
\begin{itemize}[leftmargin=16pt, itemsep=2pt]
  \item \textbf{Virtual Machine deployments} for one-tier and monolithic applications.
  \item \textbf{Kubernetes (AKS) deployments} for microservices-based architectures.
\end{itemize}
\item Developed two \textbf{e-commerce applications using the MERN stack} as real deployment use cases:
\begin{itemize}[leftmargin=16pt, itemsep=2pt]
  \item A \textbf{one-tier monolithic e-commerce application} deployed on a \textbf{Virtual Machine}, selected by the AI engine based on repository structure and runtime analysis.
  \item A \textbf{microservices-based e-commerce backend} deployed on \textbf{Kubernetes (AKS)}, recommended by the AI engine due to service decomposition and scalability requirements.
\end{itemize}
\item Automated \textbf{VM-based deployments} using \textbf{Terraform} for infrastructure provisioning, \textbf{Ansible} for configuration management, and \textbf{Docker / Docker Compose} for application delivery.
\item Implemented \textbf{AKS microservices deployments} using \textbf{AKS Engine}, \textbf{kubectl}, and Kubernetes \textbf{YAML manifests} with per-microservice deployment templates.
\item Designed and implemented \textbf{CI/CD pipelines using Jenkins}, covering build, test, quality, security, artifact management, and deployment stages.
\item Integrated \textbf{SonarQube} for code quality analysis and \textbf{Nexus} for artifact management.
\item Implemented full \textbf{observability and monitoring} using \textbf{Prometheus} and \textbf{Grafana}.
\item Reduced infrastructure provisioning and deployment time by approximately \textbf{70\%} through automation.
\end{highlights}

\textbf{Cloud and Full Stack Engineer --- Internship, RFC} \hfill Jul 2024 -- Aug 2024
\begin{highlights}
\item Developed a \textbf{cloud-native web application} for the \textbf{management of interns}, covering onboarding, tracking, and administrative workflows.
\item Deployed the application on \textbf{AWS EKS (Kubernetes)} using a fully containerized architecture.
\item Designed and implemented \textbf{end-to-end CI/CD pipelines} using \textbf{Jenkins}, \textbf{Docker}, \textbf{Terraform}, and \textbf{GitHub Actions}.
\item Implemented \textbf{IAM security controls} and \textbf{application and infrastructure monitoring} using \textbf{Prometheus} and \textbf{Grafana}.
\end{highlights}

\textbf{Web Developer --- Internship, ESPRIT} \hfill Jul 2023 -- Aug 2023
\begin{highlights}
\item Designed and developed a \textbf{web platform that scrapes official educational websites} to collect and aggregate online courses.
\item Implemented \textbf{Python-based web scraping modules} to extract course metadata such as title, provider, duration, and difficulty level.
\item Normalized and stored scraped data in a structured database for efficient search and filtering.
\item Developed backend services to rank and recommend the \textbf{best courses based on user search criteria}.
\item Built a responsive web interface allowing users to search, compare, and discover relevant courses from trusted sources.
\item Ensured data reliability by targeting only \textbf{official and verified course providers}.
\end{highlights}

\textbf{Network Engineer Intern (C-NOC) --- Tunisie Telecom} \hfill Aug 2021 -- Sep 2021
\begin{highlights}
\item Worked in the national B2B Network Operations Center.
\item Monitored enterprise network links and handled connectivity incidents.
\item Assisted in troubleshooting routing and service availability issues.
\end{highlights}

% ================= PROJECTS =================
\section{Projects}

\textbf{1. Enterprise Monitoring Platform --- Azure Stack Hub (RFC Production)}
\begin{highlights}
\item \textbf{Functional Overview:} Monitors Azure Stack Hub infrastructure health, storage fabric, and tenant VM performance (IOPS/Compute) in real-time.
\item \textbf{Engineered} an industrial-tier monitoring ecosystem for \textbf{hybrid cloud architectures} using specialized \textbf{Dockerized exporters}.
\item \textbf{Developed} high-performance \textbf{Python/Flask} micro-exporters to harvest telemetry from \textbf{Azure Stack Hub Admin APIs} via \textbf{Service Principal OAuth2} authentication.
\item \textbf{Architected} centralized \textbf{Prometheus} scraping clusters and multi-dimensional \textbf{Grafana} heatmaps, providing sub-minute visibility into region health, storage fabric, and tenant VM disk IOPS.
\item \textbf{Implemented} automated alerting thresholds and sophisticated observability metrics to minimize production downtime in sovereign cloud environments.
\end{highlights}

\textbf{2. Axynoxia ERP --- Multi-Tenant SaaS Platform}
\begin{highlights}
\item \textbf{Functional Overview:} Provides a centralized business management suite with modular CRM, inventory, and accounting tools for multi-tenant organizations.
\item \textbf{Architecting} a high-performance, \textbf{multi-tenant ERP SaaS monorepo} leveraging \textbf{NestJS}, \textbf{Prisma}, \textbf{PostgreSQL}, and \textbf{Redis}.
\item \textbf{Implementing} industrial security standards: \textbf{MFA (QR-based)}, \textbf{RBAC}, and \textbf{Argon2} encryption for sensitive business data.
\item \textbf{Orchestrating} resilient infrastructure using \textbf{Docker Compose} and \textbf{Traefik} for automated service discovery and secure tenant routing via reverse-proxy logic.
\item \textbf{Developed} an auto-discovery module system allowing business plugins (CRM, Inventory) to plug into the core without code modifications.
\end{highlights}

\textbf{3. Tickety --- High-Concurrency Enterprise Ticketing SaaS}
\begin{highlights}
\item \textbf{Functional Overview:} Facilitates large-scale event management, ticket booking, wallet transactions, and on-site ticket validation for organizers.
\item \textbf{Architected} a distributed \textbf{SaaS monorepo} (pnpm) using \textbf{React}, \textbf{NestJS}, and \textbf{Prisma}, sustaining thousands of concurrent booking transactions per second.
\item \textbf{Designed} highly normalized \textbf{PostgreSQL} schemas with optimized indexing and \textbf{Read/Write split} considerations to handle tidal-wave traffic spikes.
\item \textbf{Integrated} real-time seat inventory synchronization using \textbf{WebSockets (Socket.io)} and atomic database transactions to eliminate ticket double-booking risks.
\item \textbf{Deployed} via automated \textbf{CI/CD pipelines} with rigorous quality gates, load testing scenarios, and \textbf{Docker} containerization.
\end{highlights}

\textbf{4. Roehrdanz Immobilien --- Modern CMS and Real Estate Platform}
\begin{highlights}
\item \textbf{Functional Overview:} Manages real estate property listings, customer inquiries, and professional service presentations with an integrated admin panel.
\item \textbf{Spearheaded} the delivery of a state-of-the-art real estate platform featuring a custom \textbf{MERN-based CMS} (React 19, Express 5, MongoDB).
\item \textbf{Engineered} a robust admin control-plane for listing administration, featuring \textbf{asynchronous Base64 image processing} and dynamic SEO-optimized content rendering.
\item \textbf{Developed} a secure employee-only dashboard using \textbf{session-based authentication}, Bcryptjs hashing, and \textbf{RBAC} for content moderation.
\item \textbf{Optimized} frontend performance using \textbf{Vite} and \textbf{Tailwind CSS v4}, achieving near-instant load times for high-resolution property galleries.
\end{highlights}

\textbf{5. B-moovd --- High-Performance Mobile Ecosystem}
\begin{highlights}
\item \textbf{Functional Overview:} A high-performance mobility application for seamless booking, payment orchestration, and real-time user engagement.
\item \textbf{Engineered} a reactive, cross-platform mobile application using \textbf{Flutter}, implementing \textbf{Provider-driven state management} and fluid \textbf{60FPS animations}.
\item \textbf{Integrated} RESTful API handshakes with \textbf{Dio} and local persistent caching to ensure a seamless offline-first user experience.
\item \textbf{Optimized} application bundle size and resource allocation, ensuring high performance across a wide range of mobile hardware.
\end{highlights}

\textbf{6. Confortex --- Shopify E-commerce (confortex.shop)}
\begin{highlights}
\item \textbf{Developed} a full-featured \textbf{Shopify} e-commerce store for a premium Tunisian bedding brand, covering mattresses, pillows, beds, baby products, and linen.
\item \textbf{Configured} multi-collection product architecture, custom storefront theming, and SEO-optimized blog content to drive organic traffic.
\item \textbf{Implemented} free delivery promotions, newsletter integration, and a multi-showroom contact system across 3 physical locations in Ariana, Tunisia.
\end{highlights}

\textbf{7. Vie Sublime --- Shopify E-commerce (viesublime.tn)}
\begin{highlights}
\item \textbf{Built} a premium \textbf{Shopify} storefront for a high-end Tunisian furniture brand specializing in artisanal interior, office, outdoor, and school furniture.
\item \textbf{Structured} multi-collection catalog (Tables and Chairs, Indoor Furniture, Office, School, Garden) with custom theming aligned to a luxury brand identity.
\item \textbf{Delivered} a content-driven SEO blog, newsletter integration, and multi-location showroom management to support both online and physical sales channels.
\end{highlights}

\textbf{8. MERN E-commerce --- Industrial SaaS Infrastructure}
\begin{highlights}
\item \textbf{Functional Overview:} An industrial-grade retail platform for managing product catalogs, customer orders, and secure checkout workflows.
\item \textbf{Engineered} a full-featured e-commerce ecosystem using the \textbf{MERN} stack, focusing on industrial-grade security via \textbf{JWT} and \textbf{Argon2}.
\item \textbf{Developed} an advanced admin dashboard with real-time order tracking, inventory management, and \textbf{Multer-integrated} cloud asset handling.
\item \textbf{Implemented} responsive frontend architecture with \textbf{Redux Toolkit} for complex state persistence across purchasing workflows.
\end{highlights}

\textbf{9. OMHY Entertainment --- Managed Video Hub (\href{https://www.omhyfamily.com/}{omhyfamily.com})}
\begin{highlights}
\item \textbf{Functional Overview:} A premium digital media hub for high-fidelity video streaming, content portfolios, and interactive user experiences.
\item \textbf{Developed} a premium video-streaming and portfolio platform using \textbf{React (Chakra UI)} and \textbf{GSAP} for high-fidelity interactive animations.
\item \textbf{Orchestrated} Zero-Downtime deployments via \textbf{Jenkins} pipelines, integrating automated quality gates and security audits.
\item \textbf{Managed} hybrid database architectures (MongoDB and MySQL) to balance flexible content metadata and strict user transaction history.
\end{highlights}

\textbf{10. Jektis Travel --- Global E-Tourism Platform}
\begin{highlights}
\item \textbf{Functional Overview:} A global tourism discovery platform for booking flights and hotels with automated real-time price scraping and secure payments.
\item \textbf{Architected} an automated tourism platform in \textbf{PHP}, integrating \textbf{Stripe} for payment orchestration and custom web scraping modules for real-time discovery.
\item \textbf{Developed} automated transactional workflows using \textbf{PHPMailer} and custom cron jobs for booking status updates and guest notifications.
\end{highlights}

\textbf{11. New Journey --- Global Consulting Ecosystem}
\begin{highlights}
\item \textbf{Functional Overview:} A global consulting ecosystem to connect clients with expert advisors, managing professional interactions and service delivery.
\item \textbf{Developed} a comprehensive consulting platform utilizing \textbf{Symfony 7} and \textbf{PHP 8.2}, with a focus on modular controller architecture and \textbf{Doctrine ORM}.
\item \textbf{Implemented} dynamic UI components using \textbf{Symfony UX Turbo} and Stimulus for a high-performance, SPA-like user experience.
\item \textbf{Orchestrated} the development environment using \textbf{Docker Compose}, ensuring parity between local development and production-ready deployments.
\item \textbf{Integrated} secure multi-user authentication and role-based access control (RBAC) to manage client and admin interactions.
\end{highlights}

\textbf{12. DevOps CI/CD Hub --- Industrial Infrastructure (ESPRIT)}
\begin{highlights}
\item \textbf{Built} a full-scale CI/CD platform using \textbf{Jenkins}, \textbf{SonarQube}, and \textbf{Nexus} for versioning artifacts and code quality governance.
\item \textbf{Automated} the deployment of \textbf{Angular} and \textbf{Spring Boot} microservices with comprehensive security auditing via \textbf{Trivy}.
\end{highlights}

\textbf{13. OpenStack Private Cloud Lab --- Hybrid Infrastructure (ESPRIT)}
\begin{highlights}
\item \textbf{Deployed} a multi-node \textbf{OpenStack} private cloud, orchestrating virtual networks, subnets, and \textbf{VPN-over-physical} nodes.
\item \textbf{Managed} the entire lifecycle of virtualized workloads, implementing automated scaling and high-availability routing for guest web applications.
\end{highlights}

% ================= EDUCATION =================
\section{Education}
\textbf{Software Engineering Degree --- ESPRIT} \hfill 2020 -- 2025 \\
Ariana, Tunisia \\
3 years General Software Engineering \;|\; 2 years Specialty: \textbf{ArcTIC --- Cloud Architecture and DevOps}

% ================= LANGUAGES =================
\section{Languages}
Arabic (Native) \;|\; English (B2) \;|\; French (B2)

\end{document}