\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{black}

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust page margins
\usepackage[scale=0.9]{geometry}

% Personal data
\name{Tamim}{Hmizi}
\title{Software Engineer}
\address{Ariana, Tunisia}{}{}
\phone[mobile]{+216 21 611 816}
\email{hmizitamim@hotmail.com}
\social[linkedin]{tamimhmizi}
\social[github]{tamim-hmizi}

% Remove page numbering
\nopagenumbers{}

\begin{document}

\makecvtitle
\vspace{-14mm}
% Professional Summary
\textit{Passionate Full Stack Engineer specializing in Cloud, DevOps, and Web Development with expertise in automated infrastructure provisioning and intelligent deployment solutions}


\vspace{-2mm}
\section{Professional Experience}

\cventry{Feb 2025 -- Aug 2025}{PFE Intern - DevOps Platform Engineer}{RFC}{Ariana, Tunisia}{}{
Built auto-provisioning platform using React, Express.js, MongoDB with FastAPI backend for GitHub API analysis and LLaMA model integration. Implemented intelligent K8s/VM recommendation system and automated infrastructure provisioning with Jenkins, SonarQube, Trivy, Nexus, Docker, Terraform, Ansible, and Prometheus/Grafana monitoring.}

\cventry{Jul 2024 -- Aug 2024}{Full Stack Engineer (Cloud, DevOps, Web Development)}{RFC}{Ariana, Tunisia}{}{
Developed cloud-native applications with Next.js deployed on AWS (IAM, EKS, ECR, DynamoDB, CloudWatch). Automated CI/CD pipelines with Jenkins, Terraform, Docker, and GitHub.}

\cventry{Jul 2023 -- Aug 2023}{Web Developer}{ESPRIT}{Ariana, Tunisia}{}{
Developed search engine application using MERN stack and integrated web scraping techniques using Python.}

\cventry{Aug 2021 -- Sep 2021}{Network Engineer C-NOC}{Tunisie Telecom}{Tunis, Tunisia}{}{
Provided B2B network support and maintenance, resolved connectivity issues and performed network monitoring.}

\section{Education}
\cventry{Sep 2020 -- Aug 2025}{Software Engineering Degree}{ESPRIT}{Ariana, Tunisia}{}{}

\section{Projects}
\cventry{Sep 2024 -- Nov 2024}{DevOps Pipeline Automation}{}{}{}{CI/CD pipeline for Spring Boot with Maven, Nexus, SonarQube, Docker, Kubernetes, Terraform, JUnit, Mockito, Prometheus, Grafana.}
\cventry{Oct 2023 -- Apr 2024}{OpenStack + Kubernetes with DevOps}{}{}{}{OpenStack infrastructure, Kubernetes deployment using Ansible/Terraform, Ubuntu VMs, Angular/Spring Boot applications.}

\section{Certifications}
\cvlistitem{Microsoft Azure Fundamentals AZ-900 (Microsoft, Coursera)}
\cvlistitem{Introduction to Ansible (RedHat, Coursera)}
\cvlistitem{AWS Certified Solutions Architect - Associate (AWS, Coursera)}



\section{Technical Skills}
\cvitem{Cloud \& DevOps}{AWS, Azure, GCP, OpenStack, Docker, Kubernetes, Jenkins, Terraform, Ansible, CI/CD, IaC, Git, Monitoring}
\cvitem{Development}{Next.js, React, Angular, Express.js, Spring Boot, Python, JavaScript, Java, FastAPI, Django, Laravel}
\cvitem{Databases \& Systems}{MongoDB, DynamoDB, Linux, Windows, LLaMA, GitHub API Integration}

\section{Languages}
\cvitem{}{Arabic (Native), English (B2), French (B2)}

\end{document}
